\documentclass[letterpaper, 10pt]{article}

\usepackage{graphicx}            % Required for inserting images
\usepackage[hidelinks]{hyperref} % Required for hyperlinks
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry} % Page margins

\pagestyle{empty} % No page numbers

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\LARGE minjaesong} \\ \vspace{2pt}
    \href{mailto:thdalswo4524@g.skku.edu}{\underline{thdalswo4524@g.skku.edu}} $|$
    \href{https://github.com/thdalswo4524}{\underline{github.com/thdalswo4524}}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[] \textbf{Programming}: C, Python, JavaScript, HTML/CSS
    \item[] \textbf{Frameworks \& Tools}: Git, GitHub, LaTeX, VS Code, Claude Code
    \item[] \textbf{Languages}: Korean (Native), English (Intermediate)
\end{itemize}

%-----------EXPERIENCE-----------
\section*{Experience}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Undergraduate Student} \hfill Mar. 2025 -- Present \\
    \textit{Sungkyunkwan University} \hfill \textit{Seoul, Korea}
    \begin{itemize}
        \item Completing core CS coursework including Introduction to Algorithms, System Programming, and Open-Source Software Practice.
        \item Building personal study tools and lecture-note web applications using Git-based collaboration workflows.
    \end{itemize}
\end{itemize}

%-----------SELECTED PROJECTS-----------
\section*{Selected Projects}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Interactive Lecture Notes} \hfill Mar. 2026 -- Present \\
    \textit{Personal Project} \hfill \textit{HTML / CSS / JavaScript}
    \begin{itemize}
        \item Designed a per-subject interactive note system that converts lecture PDFs into single-file HTML pages with quizzes, simulators, and visualizations.
        \item Deployed seven independent GitHub repositories via GitHub Pages, one per course.
    \end{itemize}
    \item[]
    \textbf{Squeeze Scanner} \hfill 2025 \\
    \textit{Personal Project} \hfill \textit{Python}
    \begin{itemize}
        \item Implemented a stock-screening tool that identifies short-squeeze candidates from market data.
    \end{itemize}
    \item[]
    \textbf{Multifactor Analysis} \hfill 2024 \\
    \textit{Personal Project} \hfill \textit{Python}
    \begin{itemize}
        \item Built a quantitative multi-factor model for portfolio analysis and backtesting.
    \end{itemize}
\end{itemize}

%-----------HONORS & AWARDS-----------
\section*{Honors \& Awards}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{[Award / Scholarship Name]}, Issuing Organization \hfill Year
    \item \textbf{[Certification or Honor]}, Issuing Organization \hfill Year
\end{itemize}

%-----------EDUCATION-----------
\section*{Education}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Sungkyunkwan University} \hfill Mar. 2025 -- Present \\
    \textit{B.S. Candidate, Department of Software} \hfill \textit{Seoul, Korea}
    \begin{itemize}
        \item Relevant coursework: Introduction to Algorithms, System Programming, Open-Source Software Practice.
        \item Student ID: 2025315541.
    \end{itemize}
\end{itemize}

%-------------------------------------------
\end{document}
